Annotated example of index standardization with sdmTMB

### 2021-11-24 doc/appendix-pcod-sdmTMB.Rmd
Clean up appendix

```{r setup, include = FALSE, cache=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.asp = 0.618,
  cache = TRUE,
  autodep = TRUE
)
```

@@

```{r index, out.width="5in"}
qcs_grid$area <- 4 # all 2 x 2km
pred2 <- predict(
  fit, newdata = qcs_grid, return_tmb_object = TRUE,
  area = qcs_grid$area
)
ind <- get_index(pred2)
ggplot(ind, aes(year, est/1000)) + geom_line() +
  geom_ribbon(aes(ymin = lwr/1000, ymax = upr/1000), alpha = 0.4) +
  ylab("Biomass (t)")
```

@@

```{r index-sims, out.width="5in"}
ind <- get_index_sims(pred_sims, area = rep(4, nrow(pred_sims)), level = 0.95)
ggplot(ind, aes(year, est/1000)) + geom_line() +
  geom_ribbon(aes(ymin = lwr/1000, ymax = upr/1000), alpha = 0.4) +
  ylab("Biomass (t)")
```

>>>>

```{r setup, include = FALSE, cache=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.asp = 0.618,
  cache = TRUE,
  autodep = TRUE,
  cache.comments = FALSE
)
```

@@

```{r index, out.width="5in"}
qcs_grid$area <- 4 # all 2 x 2km
pred2 <- predict(
  fit,
  newdata = qcs_grid, return_tmb_object = TRUE,
  area = qcs_grid$area
)
ind <- get_index(pred2)
ggplot(ind, aes(year, est / 1000)) +
  geom_line() +
  geom_ribbon(aes(ymin = lwr / 1000, ymax = upr / 1000), alpha = 0.4) +
  ylab("Biomass (t)")
```

@@

```{r index-sims, out.width="5in"}
ind <- get_index_sims(pred_sims, area = rep(4, nrow(pred_sims)), level = 0.95)
ggplot(ind, aes(year, est / 1000)) +
  geom_line() +
  geom_ribbon(aes(ymin = lwr / 1000, ymax = upr / 1000), alpha = 0.4) +
  ylab("Biomass (t)")
```
